\documentclass[line,margin]{res}
\usepackage{anysize, booktabs, hyperref}
\begin{document}

%left right top bottom
\marginsize{.5in}{.5in}{.5in}{.5in}

\section{Liam Middlebrook}

\hfill email: \href{mailto:liammiddlebrook@gmail.com}{liammiddlebrook@gmail.com}
github: \href{https://github.com/liam-middlebrook}{liam-middlebrook}

\begin{resume}


\section{Skills}
\begin{table}[h]
\begin{tabular}{@{}lll@{}}
\toprule
Programming Languages & Libraries and Frameworks & Development Tools / Other   \\ \midrule
C\# (7 yrs.)          & Vulkan                   & Visual Studio (2010 - 2015) \\
C++ (4 yrs.)          & Modern OpenGL (3.3+)     & Git                         \\
GLSL (Familiar)       & Flask                    & Vim                         \\
Python (Familiar)     &                          & GNU/Linux                   \\ \bottomrule

\end{tabular}
\end{table}


\section{Work Experience}

{\textbf{\emph{NVIDIA Linux Graphics Intern}}} \hfill May 2016 - August 2016\\
Worked on implementation Vulkan Direct to Display components of VK\_DISPLAY\_KHR.

{\textbf{\emph{NVIDIA Linux Graphics Intern}}} \hfill May 2015 - August 2015\\
Worked on implementation of the next-gen Vulkan Graphics API.

{\textbf{\emph{MAGIC Research Fellow}}} \hfill March 2014 - Present\\
Worked on \href{https://github.com/liam-middlebrook/blockytalky.git}{BlockyTalky}. I implemented
the Servo Motor Block and assisted in implementing an interface for remotely controlling the
BlockyTalky through a webapp.

{\textbf{\emph{Kids On Campus Instructor}}} \hfill July 2014 - August 2014\\
Worked with students from grades 9 - 12. Over the course of two weeks each session of campers
learned how to use the Unity3D engine. The campers were taught how to create scripts for Unity
in C\#.


\section{Selected Projects}

{\textbf{\emph{Splattershmup}}} - Lead Effects Programmer\\
Splattershmup is a Shoot 'Em Up game built in WebGL and Canvas. In Splattershmup the player leaves
a trail of paint as they play, resulting in images that resemble Jackson Pollock's paintings.
I designed and implemented the paint system.
\url{http://splattershmup.rit.edu}.

{\textbf{\emph{OfCourse}}} - Contributor\\
OfCourse is a course website framework that was written in Python using the Flask library.
OfCourse is currently being used in \href{http://hfoss-fossrit.rhcloud.com}{RIT's Humanitarian
Free and Open Source Software Culture Course}. I worked on the Participants page for OfCourse
which scrapes students blogs for posts. OfCourse is part of the FOSS@MAGIC
program which is sponsored by RedHat.\\
\url{https://github.com/ryansb/ofcourse}.

{\textbf{\emph{MINX}}}\\
MINX is a C++ Game Development Framework. MINX makes it easier to create 2D games in C++ using an API
that is similar to Microsoft's XNA Framework. MINX currently runs on Windows and Linux. I created the
graphical backend for MINX and designed the API endpoints.\\
\url{https://github.com/GearChicken/MINX}

{\textbf{\emph{OpenGL Water Demo}}}\\
A demo written in C++ and OpenGL that renders water. The waves are based off of scrolling displacement
map textures. The demo includes a photo of pebbles with refraction to better demonstrate the effect
of the waves. The water in this demo is looks best when used as a background detail or with a minimal
wave amplitude.\\
\url{https://github.com/liam-middlebrook/opengl-water}


\section{Education}
{\sl Rochester Institute of Technology} \hfill August 2013 - Present

{\sl B.S. Game Design and Development, Minor in Free and Open Source Software} \hfill 3.48 GPA

\section{Activities}
Sysadmin @ Computer Science House \url{https://csh.rit.edu}, Game Developers Conference
2016, Election Night Hackathon 2014, FOSS@MAGIC, Game Developers Conference 2015,
Global Game Jam 2014, Homestretch Hackathon 2013 - 2014, Imagine Cup Hackathon 2013 - 2014,
Local Hack Day 2014, National Civic Day of Hacking 2014, Software Freedom Day 2014

%\section{References}
%Available on Request


\end{resume}
\end{document}
